Parameter Inference\\with Bifurcation Diagrams

### 2021-05-28 docs/checklist.tex

\item If you are using existing assets (e.g., code, data, models) or curating/releasing new assets...
\begin{enumerate}
  \item If your work uses existing assets, did you cite the creators?
    \answerYes{\texttt{BifurcationKit.jl} \cite{Veltz2019PseudoArcLengthContinuation.jl} for continuation, \texttt{ForwardDiff.jl} \cite{Revels2016Forward-ModeJulia} for automatic differentiation and \texttt{Flux.jl} \cite{Innes2018FashionableFlux,Innes2018Flux:Julia} for optimisation}
  \item Did you mention the license of the assets?
    \answerNo{MIT Licences}
  \item Did you include any new assets either in the supplemental material or as a URL?
    \answerYes{Julia package implementing our method \href{https://github.com/gszep/BifurcationFit.jl}{\texttt{github.com/gszep/BifurcationFit.jl}}}
  \item Did you discuss whether and how consent was obtained from people whose data you're using/curating?
    \answerNA{No data was collected}
  \item Did you discuss whether the data you are using/curating contains personally identifiable information or offensive content?
    \answerNA{No data was collected}
\end{enumerate}

>>>>

\item If you are using existing assets (e.g., code, data, models) or curating/releasing new assets...
\begin{enumerate}
  \item If your work uses existing assets, did you cite the creators?
    \answerYes{\texttt{BifurcationKit.jl} \cite{Veltz2020BifurcationKit.jl} for continuation, \texttt{ForwardDiff.jl} \cite{Revels2016Forward-ModeJulia} for automatic differentiation and \texttt{Flux.jl} \cite{Innes2018FashionableFlux,Innes2018Flux:Julia} for optimisation}
  \item Did you mention the license of the assets?
    \answerNo{MIT Licences}
  \item Did you include any new assets either in the supplemental material or as a URL?
    \answerYes{Julia package implementing our method \href{https://github.com/gszep/BifurcationFit.jl}{\texttt{github.com/gszep/BifurcationFit.jl}}}
  \item Did you discuss whether and how consent was obtained from people whose data you're using/curating?
    \answerNA{No data was collected}
  \item Did you discuss whether the data you are using/curating contains personally identifiable information or offensive content?
    \answerNA{No data was collected}
\end{enumerate}
